# Jack's text processing and scraping

* R treats strings as atomic vectors (unusual)
* like tex, use backslash for special characters EX. \n, \", etc.

```{r}
print("On two \n lines")
cat("On two \n lines")
```

## stringr package

### regex
* . : wildcard
* include hypens at the end of a list
* asterisk (*): allows for arbitrary number of things
* brackets (pattern): allows for pattern to repeat multiple times

Check out http://www.ultrapico.com/expresso.htm for regex builder

```{r}
library(stringr)

# Detect the presence or absence of a pattern in a string
str_detect("apples", "app") 

# str_extract
# str_extract_all
# str_locate  # which() for strings

 str_detect(c("dog","dig","dAg","dg","dawg"),"d[0-9a-zA-Z -]g")  # hypthen at the end
 # fits with a greedy algorithm

```

## Edit distance
Edit distance, also called Levenshtein distance, is a measure of the number of primary edits that would need to be made to transform one string into another. The R function adist() is used to find the edit distance.

* measure is symmetric, triangle inequality holds, etc.
* is the "shortest"" distance 
* case matters; can use (toupper(), built in arg, etc.)

str_trim() is also suepr useful
str_split()

EX. see the footbal example
* adist() lets us easily identify teams via distance to a set of team names
* generally robust to typos

```{r}
adist("Life isn't fair", "Fair isn't life")  # kind of dumb measure for this
adist(str_split("life isn't fair", " "), str_split("fair isn't life", " "))
```

* read in text file line by line with readLines()

## Web scraper

* note distinction between reading hyperlinks and all URLs

input_url = need "http://" in the beginning
then getHtml(input_url) # gets links

### use try() to do some error handling
var = try(function, silet = TRUE)

str_split(links, "\\?", 1)  # split at the questionmarks; keep the 1st result from the split
# https://stackoverflow.com/questions/10602433/how-to-escape-a-question-mark-in-r

## Sentiment analysis package exists
meanr package?

## Consider comparing sentences
s1 <- "The dog jumped over the cat"
s2 <- "The cat was jumped over by the dog"

str_splot(c(s1, s2), "")  # split each sentence into words, and make a matrixof distances

adist(words1, words2)

consider that order of the words matters though, 
i.e. "The cat jumped over the dog" would be mistaken for s1 if we split the words and ignore order

